---
title: "Introduction to Low Level R"
author: "Clara Barbarit"
format: html
---

```{r}
typeof(1.5)
typeof("toto")
```

### Classes
= what you create as a developer 
type = environment = what is given to you

you can create classes from a list or from a vector

```{r}
data(iris)
typeof(iris)
class(iris)
```


## Vectors
Many things in R are vector (most of the other things are list)
vector = collection of values of the same type (can be a single value)

```{r}
x <- 15.25
length(x)
x[1]
```

```{r}
y <- c(1, -2, 45, 1.5, -1e-10)
y
typeof(y)
y[2]
length(y)
```

```{r}
c(x,y)
```

```{r}
z <- "Alice"
length(z)
```

Salvation comes from the `stringr`package

```{r}
library(stringr)
```

```{r}
str_length(z)
```

```{r}
dynamite_shakers <- "🤠 🤠 🤠 🤠"
dynamite_shakers
length(dynamite_shakers)
str_length(dynamite_shakers)
```

## Indexing

```{r}
x <- c(6,5,1,2,3,4)
x[4] <- 15
x
y<-x
y
x[1] <- 18
x
y
x[c(2,2,1,4,3)]
```

Assignment can be understood has a value semantic assignment 
Index is made with vectors of any length

```{r}
x[c(-1,-4)]
```

index have to be all positive or all negative

```{r}
x[c(1,2)] <- c(-34,42)
```



